---
title: "Activity 5"
author: "Paul Nguyen"
date: "12/2/2019"
output: pdf_document
---
```{r}
library(ggplot2)
library(ggrepel)

```


```{r}
poverty <- read.delim("https://bitly.com/381pd5e")
nostate <- poverty[,-1]

twocluster <- kmeans(nostate, centers = 2)$cluster
threecluster <- kmeans(nostate, centers = 3)$cluster
fourcluster <- kmeans(nostate, centers = 4)$cluster

pca <- data.frame(prcomp(nostate)$x)
pca$K2 <- twocluster
pca$K3 <- threecluster
pca$K4 <- fourcluster

pca$State <- poverty$State


ggplot(data = poverty, mapping = aes(x = Poverty, y = Percent)) +
  geom_point()

twoclusterplot <- ggplot(data = pca, mapping = aes(x = PC1, y = PC2,
                                                   color = as.factor(K2),
                                                   label = State)) +
  geom_point() +
  geom_text_repel()
twoclusterplot
threeclusterplot <- ggplot(data = pca, mapping = aes(x = PC1, y = PC2,
                                                     color = as.factor(K3),
                                                     label = State)) +
  geom_point() +
  geom_text_repel()
threeclusterplot
fourclusterplot <- ggplot(data = pca, mapping = aes(x = PC1, y = PC2, 
                                                color = as.factor(K4),
                                                label = State)) +
  geom_point() +
  geom_text_repel()
fourclusterplot


```
What do the variables mean?
State- state
Metropolitan.Residence- percent of population living in urban area
White- percent of population that is white
Graduates- percent of population that has graduated high school
Poverty- percent of population below poverty
Percent- not sure.. seems to be pretty correlated with poverty, could be percent
of people that believe they are the below poverty threshold


